\problemname{Debugging}

\illustration{0.5}{bug}{Picture in public domain via \href{https://en.wikipedia.org/wiki/File:H96566k.jpg}{Wikimedia Commons}}%
\noindent
Your fancy debugger will not help you in this matter. There are many
ways in which code can produce different behavior between debug and
release builds, and when this happens, one may have to resort to more
primitive forms of debugging.
% -- a real coder uses them all!

So you and your printf are now on your own in the search for a line of
code that causes the release build to crash. Still you are lucky:
adding printf statements to this program affects neither the bug (it
still crashes at the same original code line) nor the execution time
(at least not notably).  So even the naive approach of putting a
printf statement before each line, running the program until it
crashes, and checking the last printed line, would work.

However, it takes some time to add each printf statement to the code,
and the program may have a lot of lines. So perhaps a better plan would involve
putting a printf statement in the middle of the program, letting it run, seeing
whether it crashes before the added line, and then continuing the search in
either the first or second half of the code.

But then again, running the program may take a lot of time, so the
most time-efficient strategy might be something in between.  Write a
program that computes the minimum worst-case time to find the crashing
line (no matter where it is), assuming you choose an optimal strategy
for placing your printf statements.

We're releasing the new version in five hours, so this issue is escalated and needs to be fixed ASAP.
%Did I already mention this issue is escalated and needs to be fixed asap?


\section*{Input}

The input consists of one line with three integers:
\begin{itemize}
\item $n$ ($1 \le n \le 10^6$), the number of code lines;
\item $r$ ($1 \le r \le 10^9$), the amount of time it takes to compile and run the program until it crashes;
\item $p$ ($1 \le p \le 10^9$), the time it takes to add a single printf line.
\end{itemize}

You have already run the program once and therefore already know that it does crash somewhere.

\section*{Output}

Output the worst-case time to find the crashing line when using an
optimal strategy.


